iPre: A Cross-platform Mobile App\\for Image Classification

### 2017-03-31 document/paper.tex
document pics to top
document grammer check

In the last few years the field of machine learning has made tremendous progress on addressing these difficult problems. In particular, it's been found that a kind of model called a deep convolutional neural network can achieve reasonable performance on hard visual recognition tasks -- matching or exceeding human performance in some domains. Basically, a model needs to be trained using existing datasets, after which the model is used to predict new inputs. However, the training process can take months to be complete for quite large training datasets. For predicting an image on a mobile device, it's inappropriate to include training process and let users wait months for results. So it would be a good idea to take advantage of pre-trained neural networks.

@@

\subsubsection{S3}
Amazon S3 (Simple Storage Service) is a web service offered by Amazon Web Services. Amazon S3 provides storage through web services interfaces.\cite{wiki:s3} The app stores all user images on S3. Once a user uploaded an image, the image would be temporarily cached on server for classification, and permanently stored in S3. In this way, it provides a stable storage and resource availability. Later on the app can display images by direct links provided by S3.

@@

\subsubsection{View Page}
Here shows the classification results of an image. It contains four parts. The first part is the image itself. The remaining parts are different representations of classification results, with each of them having five values, which are organized based on classification probabilities. These includes a pie chart, a bar chart, and a table.

@@

\subsubsection{Celery}
The app takes approximately 7 seconds to classify an image. It would not be user-friendly if it takes too long to respond. The app takes an asynchronous approach. Once an images is uploaded, it starts an asynchronous task using Celery, which executes in the background. Celery is an open source asynchronous task queue or job queue which is based on distributed message passing. While it supports scheduling, its focus is on operations in real time.\cite{wiki:flask}

@@

\subsection{Classification Model}
As mentioned above, the app uses Keras library with VGG16 model for image classification. To classify an image, firstly, VGG16 model is loaded with weights pre-trained on ImageNet. Secondly, it loads the image with target size 224 by 224. Thirdly, image data is converted to an array and been normalized. Then the image data is passed into classification model and been classified. Finally the app decodes the model outputs as different categories and gives top five 'winners' based on probabilities from high to low.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{pc_login.png}
  \caption{Log in.}
  \label{fig:pc_login}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{pc_main.png}
  \caption{Main page.}
  \label{fig:pc_main}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{pc_view.png}
  \caption{View page.}
  \label{fig:pc_view}
\end{figure}

@@

\begin{table}[h!]
  \centering
  \caption{performance on difference EC2 instance types.}
  \label{tab:table1}
  \begin{tabular}{cccc}
    \toprule
    Model & vCPU & Mem (GiB) & Time (second)\\
    \midrule
    t2.micro & 1 & 1 & 50.42\\
    t2.small & 1 & 2 & 35.87\\
    m3.medium & 1 & 3.75 & 13.25\\
    c4.large & 2 & 3.75 & 7.61\\
    c4.4xlarge & 16 & 30 & 6.12\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

In the last few years the field of machine learning has made tremendous progress on addressing these difficult problems. In particular, it's been found that a kind of model called a deep convolutional neural network can achieve reasonable performance on hard visual recognition tasks -- matching or exceeding human performance in some domains. Basically, a model needs to be trained using existing datasets, after which the model is used to predict new inputs. However, the training process can take months to be complete for quite large training datasets. For predicting an image on a mobile device, it's inappropriate to include training process and let users wait months for results. So, it would be a good idea to take advantage of pre-trained neural networks.

@@

\subsubsection{S3}
Amazon S3 (Simple Storage Service) is a web service offered by Amazon Web Services. Amazon S3 provides storage through web services interfaces.\cite{wiki:s3} The app stores all user images on S3. Once a user uploaded an image, the image would be temporarily cached on server for classification, and permanently stored in S3. In this way, it provides a stable storage and resource availability. Later on, the app can display images by direct links provided by S3.

@@

\subsubsection{View Page}
Here show the classification results of an image. It contains four parts. The first part is the image itself. The remaining parts are different representations of classification results, with each of them having five values, which are organized based on classification probabilities. These includes a pie chart, a bar chart, and a table.

@@

\subsubsection{Celery}
The app takes approximately 7 seconds to classify an image. It would not be user-friendly if it takes too long to respond. The app takes an asynchronous approach. Once an image is uploaded, it starts an asynchronous task using Celery, which executes in the background. Celery is an open source asynchronous task queue or job queue which is based on distributed message passing. While it supports scheduling, its focus is on operations in real time.\cite{wiki:flask}

@@

\subsection{Classification Model}
As mentioned above, the app uses Keras library with VGG16 model for image classification. To classify an image, firstly, VGG16 model is loaded with weights pre-trained on ImageNet. Secondly, it loads the image with target size 224 by 224. Thirdly, image data is converted to an array and been normalized. Then the image data is passed into classification model and been classified. Finally, the app decodes the model outputs as different categories and gives top five 'winners' based on probabilities from high to low.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{pc_login.png}
  \caption{Log in.}
  \label{fig:pc_login}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{pc_main.png}
  \caption{Main page.}
  \label{fig:pc_main}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{pc_view.png}
  \caption{View page.}
  \label{fig:pc_view}
\end{figure}

@@

\begin{table}[h!]
  \centering
  \caption{performance on difference EC2 instance types.}
  \label{tab:table1}
  \begin{tabular}{cccc}
    \toprule
    Model & vCPU & Mem (GiB) & Time (second)\\
    \midrule
    t2.micro & 1 & 1 & 50.42\\
    t2.small & 1 & 2 & 35.87\\
    m3.medium & 1 & 3.75 & 13.25\\
    c4.large & 2 & 3.75 & 7.61\\
    c4.4xlarge & 16 & 30 & 6.12\\
    c3.8xlarge & 32 & 60 & 6.07\\
    \bottomrule
  \end{tabular}
\end{table}
